Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-06-18 forecast/paper/supplement.Rmd
Add wide combined fig 3/4

```{r fcast, include=FALSE}
# Figure 3 in the paper
plotter(fcasts_honest %>% filter(period != "jm"), 
        "wis", Mean, scaler = "strawman_wis", 
        order_of_operations = c("aggr","scale")) +
  ylab("Mean WIS (relative to baseline)")
```

```{r hot, include=FALSE}
# Figure 4 in the manuscript
plotter_hotspots(hotspots_honest %>% filter(period != "jm")) + 
  geom_hline(yintercept = 0.5)
```

>>>>

```{r fcast, include=FALSE}
# Figure 3 in the paper
fig3 <- plotter(fcasts_honest %>% filter(period != "jm"), 
        "wis", Mean, scaler = "strawman_wis", 
        order_of_operations = c("aggr","scale")) +
  ylab("Mean WIS (relative to baseline)")
fig3
```

```{r hot, include=FALSE}
# Figure 4 in the manuscript
fig4 <- plotter_hotspots(hotspots_honest %>% filter(period != "jm")) + 
  geom_hline(yintercept = 0.5)
fig4
```

```{r fcast-hot-combo, include=FALSE, fig.width=8, fig.height=4}
leg <- get_legend(fig3)
comb1 <- plot_grid(fig3 + theme(legend.position = "none"),
                   fig4 + theme(legend.position = "none"), 
                   nrow = 1)
plot_grid(comb1, leg, ncol = 1, rel_heights = c(1,.1))
```
